Debugging of RxJS-based Applications

### 2020-09-29 paper.tex
Better Integrate Main References

Almost all participants from our interviews and war story reports showed a tendency to manually modify source code with trace logs during the hypothesis instrumentation phase when debugging RxJS code. This practice is often not perceived as efficient since the evaluation and interpretation of trace information tends to be cumbersome and very time-consuming. Also, removing log statements after a successful debugging process might leave new bugs in production code if not done carefully. We identified this technique as one of the primary debugging practices when software engineers work with RxJS-based code.

That is why we saw demand in validating this statement about manual code modification for debugging reasons with an observational study. Our study sought to validate the following hypothesis:

@@

We were able to observe how all subjects predominantly used manual source code augmentation by adding trace logs. Two of them used traditional debugging utilities in order to inspect the program's state at runtime. All subjects used the new information gained to refine their hypothesis about underlying problems before they started a new iteration in the debugging process. We could not observe the extraction to and reintegration from an external tool. All subjects exhibited the debugging behavior described in our hypothesis.

Even though two subjects stated in the after-action survey to regularly use rxjs-spy for debugging RxJS programs, neither S1 nor S3 made use of this library during the experiment part of the study.

@@

The best RP debugging tools are useless if either the hurdle to use them is too high, or engineers do not understand in which particular part of the debugging process they can benefit from them. Hence, we are able to postulate an answer to our first research question RQ1: The most significant challenge software engineers face when debugging RxJS-based programs is to know \emph{when} they should apply \emph{what} tool to resolve their current problem in the \emph{most efficient} way.

>>>>

Almost all participants from our interviews and war story reports showed a tendency to manually modify source code with trace logs during the hypothesis instrumentation phase when debugging RxJS code. This practice is often not perceived as efficient since the evaluation and interpretation of trace information tends to be cumbersome and very time-consuming. Also, removing log statements after a successful debugging process might leave new bugs in production code if not done carefully. We identified this technique as one of the primary debugging practices when software engineers work with RxJS-based code, which supports earlier results by Banken et al. \cite{10.1145/3180155.3180156} further.

That is why we saw demand in validating this statement and previous findings about manual code modification for debugging reasons with an observational study. Our study sought to validate the following hypothesis:

@@

We were able to observe how all subjects predominantly used manual source code augmentation by adding trace logs, which confirmed previous results by Banken et al. \cite{10.1145/3180155.3180156}. Two of the subjects used traditional debugging utilities in order to inspect the program's state at runtime in addition. All subjects used the new information gained to refine their hypothesis about underlying problems before they started a new iteration in the debugging process. We could not observe the extraction to and reintegration from an external tool. All subjects exhibited the debugging behavior described in our hypothesis.

Even though S1 and S3 stated in the after-action survey to regularly use rxjs-spy for debugging RxJS programs, neither of them made use of this library during the experiment part of the study.

@@

The best RP debugging tools are useless if either the hurdle to use them is too high, or engineers do not understand which particular part of the debugging process they can benefit from them. Salvaneschi et al. \cite{10.1145/2884781.2884815} provided in their previous study on \emph{Reactive Inspector} for \emph{REScala} evidence on the effectiveness of a fully integrated RP debugging solution, which supports developers in their daily work using the Eclipse IDE. Hence, we can postulate an answer to our first research question RQ1: The most significant challenge software engineers face when debugging RxJS-based programs is to know \emph{when} they should apply \emph{what} tool to resolve their current problem in the \emph{most efficient} way.
